Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-31 paper/paper.tex
cleaner plots

          ymax=28000,

@@

          symbolic x coords={content, flow, pcre, flowbits, threshold, dsize, itype, icode, flags, tls.fingerprint},          

@@

        \addplot coordinates {(content,25699) (flow,23159) (pcre,10181) (flowbits,3049) (threshold,2300) (dsize,882) (itype,155) (icode, 108) (flags, 97) (tls.fingerprint, 61)};

@@

          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},

@@

          \addplot coordinates {(0,2134) (1,9164) (2,5103) (3,5841) (4,1987) (5,1622) (6,805) (7, 535) (8, 340) (9,154) (10, 53)};

@@

          symbolic x coords={GET, POST, SELECT, UNION, id=, DELETE, UPDATE, INSERT, 200, /index.php?},          

@@

        \addplot coordinates {(GET,2007) (POST,1570) (SELECT,747) (UNION,461) (id=,408) (DELETE,390) (UPDATE,387) (INSERT, 386) (200, 352) (/index.php?, 273)};

>>>>

          ymax=27000,

@@

          %symbolic x coords={content, flow, pcre, flowbits, threshold, dsize, itype, icode, flags, tls.fingerprint},          
          symbolic x coords={content, flow, pcre, flowbits, threshold, dsize, itype},          

@@

        \addplot coordinates {(content,25699) (flow,23159) (pcre,10181) (flowbits,3049) (threshold,2300) (dsize,882) (itype,155)};

@@

          %symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7},

@@

          \addplot coordinates {(0,2134) (1,9164) (2,5103) (3,5841) (4,1987) (5,1622) (6,805) (7, 535)};

@@

          %symbolic x coords={GET, POST, SELECT, UNION, id=, DELETE, UPDATE, INSERT, 200, /index.php?},          
          symbolic x coords={GET, POST, SELECT, UNION, id=, DELETE, UPDATE},          

@@

        \addplot coordinates {(GET,2007) (POST,1570) (SELECT,747) (UNION,461) (id=,408) (DELETE,390) (UPDATE,387)};
